---
title: "Temperature: Alpha Diversity Analysis"
author: "Michael Sieler"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Global Variables

This chunk of code grabs the relevant data frames/tables generated from the `microbiomeProcessing.R` script for analysis.

```{r}

df.conT0TF %>%
  filter(DPE == 0) %>%
  group_by(Temperature, Treatment) %>%
  count()

data <- df.conT0TF
data.alpha <- dt.alphaPlus.conT0TF.melt
ps.obj <- ps.conT0TF
dist <- distList.conT0TF
# data.diffAb <- diffAb.conT0TF

data.alpha <- 
  data.alpha %>%
    mutate(Temperature = as.factor(Temperature),
           DPE = as.factor(DPE)
           )


levels(data.alpha$Temperature) <- factor(levels(data.alpha$Temperature), levels = c(28, 32, 35))
data.alpha$Temperature <- relevel(factor(data.alpha$Temperature), ref = "28")
# data.alpha$Temperature

levels(data.alpha$DPE) <- factor(levels(data.alpha$DPE), levels = c(0, 14, 21, 28, 42))
data.alpha$DPE <- relevel(factor(data.alpha$DPE), ref = "0")
# data.alpha$DPE
```

### Alpha Diversity

Saves images to following directory

```{r}

tmp.path <- "Temp/Alpha"
# Plot settings
gg_record(dir = file.path(path.results, tmp.path),
          device = "png",
          width = 5,
          height = 5,
          units = "in"
          )


```

#### Temp

```{r Temp_Alpha, fig.width=5, fig.height=4.5}

# library(multcomp)
# Source: https://stats.stackexchange.com/a/60361
# Source: https://cran.r-project.org/web/packages/multcomp/vignettes/multcomp-examples.pdf

tukey.test.list <- lapply(methods.alpha, function(alpha){
  summary(multcomp::glht(glm(formula = Alpha.Score ~ -1 + Temperature, 
                             data = data.alpha %>% filter(Alpha.Metric == alpha),
                             family = "quasibinomial"), 
                             linfct = mcp(Temperature = "Tukey")) ) %>% 
  tidy() %>%
  separate(contrast, c('group1', 'group2'), sep = " - ") %>%
  select(-c(null.value)) %>%
  rename(p.adj = adj.p.value) %>%
  mutate(p.adj.signif = case_when(p.adj < 0.05 ~ "*",
                                  p.adj >= 0.05 ~ "ns")) %>%
  mutate(`.y.` = "Alpha.Score", .after = 1) %>%
  mutate(metric = alpha, .before = 1)
})


plot.sig.labs <- lapply(methods.alpha, function(alpha){ 
  tukey.test.list[[alpha]] %>% 
  as_tibble() %>% 
  select(`.y.`, group1, group2, p.adj.signif)
})


numStatSigComp(plot.sig.labs[["Simpson"]])
seqStatSigComp(plot.sig.labs[["Simpson"]])
tail(seqStatSigComp(plot.sig.labs[["Simpson"]]), n = 1)

lapply(methods.alpha, function(alpha){ 
  seqStatSigComp(plot.sig.labs[[alpha]])
})

lapply(methods.alpha, function(alpha){ 
  data.alpha %>%
  filter(Alpha.Metric == alpha) %>%
    ggplot(aes(x = Temperature, 
               y = Alpha.Score
               )) +
    geom_boxplot(aes(fill = Temperature), outlier.shape = NA) +
    geom_quasirandom(size = 1) +
    scale_fill_manual(values = col.Temp) +
    scale_color_manual(values = col.Temp) + 
    labs(
      # title = "",
      caption = paste0(alpha," (Controls)"),
      # caption = paste0(alpha),
      x = "Temperature",
      y = "Alpha Score (normalized)"
    ) +
  theme(legend.position = "bottom")
})



# Stats

# Build GLM Model
mod.list <- lapply(methods.alpha, function(alpha){
  glm( formula = "Alpha.Score ~ Temperature",
       data = subset(data.alpha, Alpha.Metric == alpha),
       family = "quasibinomial")
}) %>% setNames(methods.alpha)

# Model Output
lapply(methods.alpha, function(x){
  mod.list[[x]] %>% 
    tidy() %>%
    mutate(metric = x, .before = 1) %>%
      mutate(sig = ifelse(p.value <= 0.05, "*", ""))
}) %>% bind_rows() %>%
  flextable() %>%
  colformat_double(j = 3:5, digits = 3) %>%
  merge_v(j = 1)  %>%
  set_formatter(values = list("p.value" = p_val_format) ) %>%
  hline(i = c(3,6,9), j = NULL, border = NULL, part = "body") %>%
  set_caption(paste0("glm(Alpha.Score ~ Temperature), family = quasibinomial)")) %>%
  autofit() #%>%
  # save_as_image(path = file.path(path.results, tmp.path, "GLM-Mod_Alpha-Temperature_Ctrl.png"))

# Anova
lapply(methods.alpha, function(x){
  mod.list[[x]] %>% Anova(type = 2) %>%
    tidy() %>%
    mutate(metric = x, .before = 1)  %>%
      mutate(sig = ifelse(p.value <= 0.05, "*", ""))
}) %>% bind_rows() %>%
    flextable() %>%
    # align(j = 3:6, align = "right") %>%
    colformat_double(j = 3, digits = 3) %>%
    merge_v(j = 1) %>%
    set_formatter(values = list("p.value" = p_val_format) ) %>%
    set_caption(paste0("ANOVA( glm(Alpha.Score ~ Temperature), family = quasibinomial) )")) %>%
    autofit() #%>%
  # save_as_image(path = file.path(path.results, tmp.path, "ANOVA_Alpha-Temperature_Ctrl.png"))

# Tukey's Pairwise Comparison
tukey.test.list %>%
  bind_rows() %>%
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:9, digits = 3) %>%
  merge_v(j = 1) %>%
  set_formatter(values = list("adj.p.value" = p_val_format) ) %>%
  hline(i = c(3,6,9), j = NULL, border = NULL, part = "body") %>%
  set_caption(paste0("Pairwise Tukey's HSD, p.adj: Dunnett. glm(Alpha.Score ~ Temperature), family = quasibinomial)")) %>%
  autofit() #%>%
  # save_as_image(path = file.path(path.results, tmp.path, "Tukeys_Alpha-Temperature_Ctrl.png"))




```

#### Temp:DPE


```{r Temp-DPE_Alpha, fig.width=5, fig.height=4.5}

tukey.test.list <- lapply(methods.alpha, function(alpha){
  test <- data.alpha %>%
    filter(Alpha.Metric == alpha) %>%
    group_by(Temperature) %>%
    nest(data = -Temperature) %>%
    mutate(test = map(.x=data, 
                      ~summary(multcomp::glht(glm(formula = Alpha.Score ~ -1 + DPE, 
                           data = .x,
                           family = "quasibinomial"), 
                           linfct = mcp(DPE = "Tukey")) )%>% tidy
                      )) %>%
    unnest(test) %>%
    separate(contrast, c('group1', 'group2'), sep = " - ") %>%
    select(-c(data, null.value)) %>%
    rename(p.adj = adj.p.value) %>%
    mutate(p.adj.signif = case_when(p.adj < 0.05 ~ "*",
                                    p.adj >= 0.05 ~ "ns")) %>%
    mutate(`.y.` = "Alpha.Score", .after = 1) %>%
    arrange(Temperature)%>%
  mutate(metric = alpha, .before = 1)
})



plot.sig.labs <- lapply(methods.alpha, function(alpha){ 
  tukey.test.list[[alpha]] %>% 
  as_tibble() %>% 
  select(Temperature, `.y.`, group1, group2, p.adj.signif)
})




lapply(methods.alpha, function(alpha){ 
  data.alpha %>%
  filter(Alpha.Metric == alpha) %>%
    ggplot(aes(x = DPE, 
               y = Alpha.Score
               )) +
    geom_boxplot(aes(fill = Temperature)) +
    geom_quasirandom(size = 1) +
    facet_grid(. ~ Temperature, scale = "free") +
    scale_fill_manual(values = col.Temp) +
    # scale_color_manual(values = pal.Set1) +
    labs(
      # title = "",
      caption = paste0(alpha," (Controls)"),
      x = "Days Post Exposure (DPE)",
      y = "Alpha Score (normalized)"
    ) +
  theme(legend.position = "none")

})
  

# Stats

# Build GLM Model
mod.list <- lapply(methods.alpha, function(alpha){
  glm( formula = "Alpha.Score ~ Temperature*DPE",
       data = subset(data.alpha, Alpha.Metric == alpha),
       family = "quasibinomial")
}) %>% setNames(methods.alpha)

 # Model Output
lapply(methods.alpha, function(x){
  mod.list[[x]] %>% 
    tidy() %>%
    mutate(metric = x, .before = 1) %>%
      mutate(sig = ifelse(p.value <= 0.05, "*", ""))
}) %>% bind_rows() %>%
  flextable() %>%
  colformat_double(j = 3:5, digits = 3) %>%
  merge_v(j = 1)  %>%
  set_formatter(values = list("p.value" = p_val_format) ) %>%
  hline(i = seq(4,12,4), j = NULL, border = NULL, part = "body") %>%
  set_caption(paste0("glm(Alpha.Score ~ Temperature*Time), family = quasibinomial)")) #%>%
  # save_as_image(path = file.path(path.figures, tmp.path, "GLM_Alpha-TempDPE_Ctrl.png"))

# Anova
lapply(methods.alpha, function(x){
  mod.list[[x]] %>% Anova(type = 2) %>%
    tidy() %>%
    mutate(metric = x, .before = 1)  %>%
      mutate(sig = ifelse(p.value <= 0.05, "*", ""))
}) %>% bind_rows() %>%
    flextable() %>%
    # align(j = 3:6, align = "right") %>%
    colformat_double(j = 3, digits = 3) %>%
    merge_v(j = 1) %>%
    hline(i = c(3,6,9), j = NULL, border = NULL, part = "body") %>%
    set_formatter(values = list("p.value" = p_val_format) ) %>%
    set_caption(paste0("ANOVA( glm(Alpha.Score ~ Temperature*Time), family = quasibinomial) )")) %>%
    autofit() #%>%
  # save_as_image(path = file.path(path.figures, tmp.path, "ANOVA_Alpha-TempDPE_Ctrl.png"))

# Tukey's Pairwise Comparison
tukey.test.list %>%
  bind_rows() %>%
  flextable() %>%
  align(j = 3:6, align = "right") %>%
  colformat_double(j = 6:9, digits = 3) %>%
  merge_v(j = c(1,2)) %>%
  set_formatter(values = list("p.adj" = p_val_format) ) %>%
  hline(i = seq(10,110, by = 10), j = NULL, border = NULL, part = "body") %>%
  set_caption(paste0("Pairwise Tukey's HSD, p.adj: Dunnett. glm(Alpha.Score ~ Temperature:DPE), family = quasibinomial)")) %>%
  autofit() #%>%
  # save_as_image(path = file.path(path.figures, tmp.path, "Tukeys_Alpha-TempDPE_Ctrl.png"))


```

### Troubleshooting

Check for possible confounding factors that might influence the data.

#### Tank Effects?

##### At 0 DPE

```{r, fig.width=5, fig.height=2}

lapply(methods.alpha, function(alpha){ 
  data.alpha %>%
  filter(Alpha.Metric == alpha &
         DPE == 0) %>%
    ggplot(aes(x = factor(Tank.ID), 
               y = Alpha.Score
               )) +
    geom_boxplot(aes(fill = factor(Tank.ID))) +
    geom_quasirandom(size = 1) +
    facet_grid(. ~ Temperature, scale = "free") +
    scale_fill_manual(values = c(pal.Set1, pal.Dark2)) +
    scale_color_manual(values = c(pal.Set1, pal.Dark2)) +
    labs(
      # title = "",
      caption = paste0(alpha," (Controls, 0 DPE)"),
      x = "Tanks",
      y = "Alpha Score (normalized)"
    ) +
  theme(legend.position = "none")

})

mod.list <- lapply(methods.alpha, function(alpha){
  glm( formula = "Alpha.Score ~ Temperature + Tank.ID",
       data = subset(data.alpha, Alpha.Metric == alpha & DPE == 0),
       family = "quasibinomial")
}) %>% setNames(methods.alpha)

lapply(methods.alpha, function(x){
  mod.list[[x]] %>% Anova(type = 2) %>%
    tidy() %>%
    mutate(metric = x, .before = 1)  %>%
      mutate(sig = ifelse(p.value <= 0.05, "*", ""))
}) %>% bind_rows() %>%
    flextable() %>%
    # align(j = 3:6, align = "right") %>%
    colformat_double(j = 3, digits = 3) %>%
    merge_v(j = 1) %>%
    hline(i = c(2,4,6), j = NULL, border = NULL, part = "body") %>%
    set_formatter(values = list("p.value" = p_val_format) ) %>%
    set_caption(paste0("ANOVA( glm(Alpha.Score ~ Temperature + Tank.ID), family = quasibinomial) )")) %>%
    autofit()


```


##### Across all control samples and DPE

```{r, fig.width=5, fig.height=2.25}

data.alpha %>%
  group_by(Alpha.Metric, Tank.ID) %>%
  count()

lapply(methods.alpha, function(alpha){ 
  data.alpha %>%
  filter(Alpha.Metric == alpha) %>%
    ggplot(aes(x = factor(Tank.ID), 
               y = Alpha.Score
               )) +
    geom_boxplot(aes(fill = factor(Tank.ID))) +
    geom_quasirandom(aes(color = Treatment), shape =21, size = 1) +
    facet_grid(. ~ Temperature, scale = "free") +
    scale_fill_manual(values = c(pal.Set1, pal.Dark2)) +
    scale_color_manual(values = c("black", "grey")) +
    labs(
      # title = "",
      caption = paste0(alpha," (Controls, 0-42 DPE)"),
      x = "Tanks",
      y = "Alpha Score (normalized)"
    ) +
  theme(legend.position = "none")

})

mod.list <- lapply(methods.alpha, function(alpha){
  glm( formula = "Alpha.Score ~ Temperature + Tank.ID",
       data = subset(data.alpha, Alpha.Metric == alpha),
       family = "quasibinomial")
}) %>% setNames(methods.alpha)

lapply(methods.alpha, function(x){
  mod.list[[x]] %>% Anova(type = 2) %>%
    tidy() %>%
    mutate(metric = x, .before = 1)  %>%
      mutate(sig = ifelse(p.value <= 0.05, "*", ""))
}) %>% bind_rows() %>%
    flextable() %>%
    # align(j = 3:6, align = "right") %>%
    colformat_double(j = 3, digits = 3) %>%
    merge_v(j = 1) %>%
    hline(i = c(2,4,6), j = NULL, border = NULL, part = "body") %>%
    set_formatter(values = list("p.value" = p_val_format) ) %>%
    set_caption(paste0("ANOVA( glm(Alpha.Score ~ Temperature + Tank.ID), family = quasibinomial) )")) %>%
    autofit()


```

## Testing MicroViz Functions

### Working


```{r message=FALSE, warning=FALSE}
test <-
  ps.obj %>%
    ps_calc_diversity(
    rank = "Taxon",
    index = "shannon",
    exp = T
    ) %>% ps_calc_diversity(
    rank = "Taxon",
    index = "inverse_simpson"
    ) %>% ps_calc_richness(
    rank = "Taxon",
    ) %>% ps_calc_diversity.phy() %>%
    ps_mutate(across(contains("_Taxon"), rescale_values, .names = "{.col}_norm"))

test %>% sam_data() 

```








### Testing


```{r}

test.ps.obj <- ps.obj

df.ps.phy <- picante::pd(samp = otu.matrix(ps.obj), tree = phyloseq::phy_tree(ps.obj)) %>% 
  # as_tibble(
  #   # rownames = "Sample"
  #   ) %>%
  rename(phylogenetic = PD,
         richness = SR) %>%
  select(-richness)

df.ps.phy[[".rownames."]] <- rownames(df.ps.phy)

test.ps.obj %>% sample_data()
df.ps.phy

test.ps.phy.join <- 
  test.ps.obj %>%
    ps_select(-Sample) %>%
    ps_join(
        x = ., y = df.ps.phy, type = "left", .keep_all_taxa = TRUE,
        match_sample_names = ".rownames.", keep_sample_name_col = FALSE
      )

test.ps.phy.join %>% sample_data()
  
```


```{r}


test %>%
  ps_mutate(phylogenetic_Taxon_norm = scales::rescale(phylogenetic_Taxon, to = c(0, 1)) ) %>%
  sample_data()

test %>%
  sample_data() %>%
  as_tibble() %>%
  select(contains("_Taxon")) %>%
  map(scales::rescale(., range = c(0, 1)) )

sample.data.frame(test) %>%
  mutate(across(contains("_Taxon"), rescale_values, .names = "{.col}_norm"))

test <- 
test %>%
  ps_mutate(across(contains("_Taxon"), rescale_values, .names = "{.col}_norm")) #%>% sample_data()

test 

rescale_values <- function(x) {
  
  ### Example Function ###
  # 
  # test %>%
  #   ps_mutate(across(contains("_Taxon"),  ## Grab columns with this substring
  #                    rescale_values, ## THIS is the function
  #                    .names = "{.col}_norm"))  ## add columns and rename appending '_norm" 
  # 
  #######
  
  if (nortest::ad.test(x)$p.value <= 0.05) {
      # If the alpha scores do not follow a normal distribution, then you transform it using Tukey's (not Turkey's) power of ladders
  #   - This will transform your data as closely to a normal distribution
  
  # Sub-function to transform data that isn't normally distributed using Tukey's (not Turkey's) power of ladders
  #   - Check this out for more info: ?transformTukey()
  x.trans <- rcompanion::transformTukey(x, plotit = F, quiet = F, statistic = 2)
  
  x.trans.norm <- (x.trans-min(x.trans))/(max(x.trans)-min(x.trans))   # Fixes normalization 0 to 1
  
  # Runs ad.test again to see if data returns higher than 0.05 p-value, if true then it transforms your data along tukey's power of ladders
  
  if (nortest::ad.test(x.trans.norm)$p.value < 0.05) {
    
    x.trans.norm <- (x.trans.norm - min(x.trans.norm ))/(max(x.trans.norm )-min(x.trans.norm )) 
    
      # Sends your data back normalized from 0 to 1
      return(x.trans.norm)
    
    # If your data is now normally distributed it will return < 0.05 p.val, and then it uses max/min values to distribute the scores along a 0 and 1 scale.
  } else {
    
    # Sends your data back normalized from 0 to 1
    return(x.trans.norm)
  }
  
  # If your data is already normally distributed, then it uses max/min values to distribute the scores along a 0 and 1 scale.
  } else {
    
    x.norm <- (x - min(x ))/(max(x )-min(x ))  # Fixes normalization 0 to 1
    # print(paste0("Finished: ", alpha))  # Letting you know what it's working on
    return(x.norm)
  }
    
}

test %>%
  sample.data.frame() %>%
  pivot_longer(.,cols = contains("_Taxon_norm"), names_to = "alpha.metric", values_to = "alpha.score") %>%
  ggplot(aes(x = alpha.score)) + 
  geom_histogram(aes(fill = alpha.metric))

test %>%
  sample.data.frame() %>%
  pivot_longer(.,cols = contains("_Taxon_norm"), names_to = "alpha.metric", values_to = "alpha.score") %>%
  group_by(alpha.metric) %>%
  summarize(min = min(alpha.score),
            max = max(alpha.score),
            mean = mean(alpha.score),
            median = median(alpha.score)
            )

test %>%
  sample.data.frame() %>%
  filter(Treatment == "Control") %>%
  pivot_longer(.,cols = ends_with("_Taxon_norm"), names_to = "alpha.metric", values_to = "alpha.score") %>%
  filter(alpha.metric == "phylogenetic_Taxon_norm") %>%
  ggplot(aes(x = factor(DPE), y = alpha.score, fill = factor(DPE))) + 
  geom_boxplot()# +
  # facet_grid(factor(Temperature) ~ alpha.metric)

test %>%
  sample.data.frame() %>%
  filter(Treatment == "Control") %>%
  pivot_longer(.,cols = ends_with("_Taxon_norm"), names_to = "alpha.metric", values_to = "alpha.score") %>%
  # filter(alpha.metric == "phylogenetic_Taxon_norm") %>%
  ggplot(aes(x = factor(DPE), y = alpha.score, fill = factor(DPE))) + 
  geom_boxplot() +
  facet_grid(factor(Temperature) ~ alpha.metric)

```



# Test function

```{r}

test <-
  ps.obj %>%
    ps_calc_diversity(
    rank = "Taxon",
    index = "shannon",
    exp = T
    ) %>% ps_calc_diversity(
    rank = "Taxon",
    index = "inverse_simpson"
    ) %>% ps_calc_richness(
    rank = "Taxon",
    ) %>% ps_calc_diversity.phy() %>%
    ps_mutate(across(contains("_Taxon"), rescale_values, .names = "{.col}_norm"))

test %>% sam_data() 
  




```


```{r}


# Load the phyloseq object
ps.obj <- readRDS("phyloseq_object.rds")

# Extract the OTU table from the phyloseq object
otu_table <- otu_table(ps.obj)

# Calculate the alpha diversity using Shannon Index
alpha_diversity <- diversity(ps.obj, index = "shannon")

# Print the results
print(alpha_diversity)


```



